Efficient Calculation of Polynomial and Interaction Features on Sparse Matrices

### 2015-09-21 paper/paper2.tex
need john's proof

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We give an algorithm to efficiently calculate second degree polynomial or interaction 
that has complexity quadratically (with respect to the density of the matrix) better than 
the naive approach and allows for the matrix to remain in sparse form. We apply the method
to several real datasets and give both analytical and empirical comparisons with the
naive approach.
\end{abstract}

>>>>

\begin{abstract}%   <- trailing '%' for backward compatibility of .sty file
We give an algorithm to efficiently calculate second degree polynomial or interaction 
that has complexity quadratically with respect to the density of the matrix, and can therefore be much faster than 
the naive approach and allows for the matrix to remain in sparse form. We apply the method
to several real datasets and give both analytical and empirical comparisons with the
naive approach.
\end{abstract}
